Supporting Information:\\ Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-06-20 Manuscript/manuscriptPSsuppl.tex
Unifying author contributions

\noindent
{\it Batuhan Kav}
set up, performed, and analysed Amber Lipid14/17 simulations with the Amber MD.

@@

\noindent
{\it Josef Melcr}
consulted the project, 
prepared tools for calculating order parameters,
and performed several simulations.

@@

\noindent
{\it Ricky Nencini}
ran the simulations of POPC systems using CHARMM36 with and without NB-Fix, and contributed to the discussion on system/bulk concentration.

>>>>

\noindent
{\it Batuhan Kav}
set up, performed, and analysed Amber Lipid14/17 simulations with the Amber MD simulation package.

@@

\noindent
{\it Josef Melcr}
prepared tools for calculating order parameters, performed Lipid14/17 simulations with Gromacs MD simulation package,
and provided comments on the manuscript.

@@

\noindent
{\it Ricky Nencini}
ran the simulations of POPC systems using CHARMM36 with and without the NB-Fix corrections,
and analyzed the difference between bulk and buffer concentrations.
